Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-28 paper.tex
Add diagrams of smart contracts

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contact, which maintains all participants' information, including their DID (Decentralized Identifiers) information and public keys. Then some preselected brokers who are trustworthy are added to the decentralized data marketplace. Anyone who would like to sell or purchase data may register to become the data providers or consumers. The registrar has the authority to agree with applications.

\subsection{Launching and Searching Products}
To sell the sensing data, a data provider has to launch a new product on the data marketplace in advance. The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract.

>>>>

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contact (Figure \ref{fig:registration_contract}), which maintains all participants' information, including their DID (Decentralized Identifiers) information and public keys. Then some preselected brokers who are trustworthy are added to the decentralized data marketplace. Anyone who would like to sell or purchase data may register to become the data providers or consumers. The registrar has the authority to agree with applications.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{registration_contract}
	\caption{Registration Contract.}
	\label{fig:registration_contract}
\end{figure}

\subsection{Launching and Searching Products}
To sell the sensing data, a data provider has to launch a new product on the data marketplace in advance. The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract (Figure \ref{fig:product_contract}).

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{product_contract}
\caption{Product Contract.}
\label{fig:product_contract}
\end{figure}
